---
title: "advanced-statistics"
author: "Erin M. Buchanan"
date: "3/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Advanced Statistics

**Course Description:** This course is a survey course over topics of the use of statistics in psychology, which will cover advanced statistical procedures from ANOVA (between, repeated measures, multivariate), regression (multiple, log linear), and pictures (canonical correlation, multidimensional scaling, factor analysis). Not all analyses are used in teaching the course, as other videos and designs are grouped with this page. You can find the files for these videos in the _other_ folder of the downloadable set. My dummies guides for _R_ and SPSS with write up examples are also included in these folders.

- **Cite**: Buchanan, E. M. (2020, March 14). Advanced Statistics. https://doi.org/10.17605/OSF.IO/DNUYV 
- **OSF Page**: https://osf.io/dnuyv/
- **GitHub Page**: https://github.com/doomlab/statsofdoom-files/tree/master/advanced

```{r echo = F, message = F}
library(rio)
library(kableExtra)
library(dplyr)
page <- "advanced"

yt_data <- import(paste0(here::here(), "/no_sync/youtube_updated.xlsx"))

yt_data <- subset(yt_data, page == page)
```

### SPSS & VassarStats

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "SPSS" | program == "na") %>% 
        filter(order != "extra") %>% 
        arrange(-desc(as.numeric(order))) %>%
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary>

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "SPSS" | program == "na") %>% 
        filter(order == "extra") %>% 
        arrange(desc(section)) %>% 
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>

### *R* 

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(order != "extra") %>% 
        arrange(-desc(as.numeric(order))) %>%
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary>

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(order == "extra") %>% 
        arrange(desc(section)) %>% 
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>

### JASP & Excel

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(order != "extra") %>% 
        arrange(-desc(as.numeric(order))) %>%
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary>

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(order == "extra") %>% 
        arrange(desc(section)) %>% 
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>
