---
comments: false
---

## Basic Statistics

**Course description**: Principles and methods of statistics used in psychology; understanding and interpreting psychological data. Typically covers descriptive statistics, hypothesis testing, z-tests, t-tests, ANOVA, correlation, regression, and chi-square analyses. 

**Course Schedule for a 15-week Fall/Spring Semester:** The following table provides a proposed 15-week schedule for a fall or spring semester. Materials follow the Nolan and Heinzen _Statistics for the Behavioral Sciences_; however, course materials are also provided from the Aron, Aron, and Coups _Statistics for Psychology_. Video links from the YouTube channel are attached to match course materials. Please use the GitHub Repository for most up to date files.

SPSS and R Course Files: 

- **Cite**: Buchanan, E. M. (2017, November 14). Basic Statistics. Retrieved from osf.io/e3d9w 
- **OSF Page**: https://osf.io/e3d9w/
- **GitHub Page**: https://github.com/doomlab/statsofdoom-files/tree/master/basics

JASP Course Files:

- **Cite**: Buchanan, E. M., Hopke, T. G., & Donaldson, S. (2018, November 27). Undergraduate Statistics with JASP. https://doi.org/10.17605/OSF.IO/T56KG 
- **OSF Page**: https://osf.io/t56kg/
- **GitHub Page**: https://github.com/doomlab/statsofdoom-files/tree/master/basics

```{r echo = F, message = F}
library(rio)
library(kableExtra)
library(dplyr)
page <- "basics"

yt_data <- import(paste0(here::here(), "/no_sync/youtube_updated.xlsx"))

yt_data <- subset(yt_data, page == page)
```

### SPSS & VassarStats

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "SPSS" | program == "na") %>% 
        filter(order != "extra") %>% 
        arrange(-desc(as.numeric(order))) %>%
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary>

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "SPSS" | program == "na") %>% 
        filter(order == "extra") %>% 
        arrange(desc(section)) %>% 
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>

### *R* 

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(order != "extra") %>% 
        arrange(-desc(as.numeric(order))) %>%
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary>

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(order == "extra") %>% 
        arrange(desc(section)) %>% 
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>

### JASP & Excel

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(order != "extra") %>% 
        arrange(-desc(as.numeric(order))) %>%
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary>

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(order == "extra") %>% 
        arrange(desc(section)) %>% 
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>