---
comments: false
pagetitle: 'Graduate Statistics'
---

## Graduate Statistics 

**Course Description:** Use of the Analysis of Variance (ANOVA) Models and Multivariate Analysis in the design and analysis of psychological experiments. Topics include correlation, regression, t-test, ANOVA (between, repeated, and mixed), mediation, moderation, and exploratory factor analysis. 

**Course Schedule for a 15-week Fall/Spring Semester:** The following table provides a proposed 15-week schedule for a fall or spring semester. Materials follow the Field _Discovering Statistics using R/SPSS_; however, course materials are also provided from the Keppel and Wickens _Design and Analysis_. Video links from the YouTube channel are attached to match course materials. Years are included when there are multiple versions of the videos - R commands often update, and new videos reflect those changes.

- **Cite**: Buchanan, E. M. (2020, March 15). Graduate Statistics. https://doi.org/10.17605/OSF.IO/X5GNJ 
- **OSF Page**: https://osf.io/x5gnj/
- **GitHub Page**: https://github.com/doomlab/statsofdoom-files/tree/master/graduate

```{r echo = F, message = F}
library(rio)
library(kableExtra)
library(dplyr)
page <- "graduate"

yt_data <- import(paste0(here::here(), "/no_sync/youtube_updated.xlsx"))

yt_data <- yt_data[!is.na(yt_data$graduate), ]
```

### SPSS & VassarStats

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "SPSS" | program == "na") %>% 
        filter(graduate_order != "extra") %>% 
        arrange(-desc(as.numeric(graduate_order))) %>%
        select(graduate, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary>

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "SPSS" | program == "na") %>% 
        filter(graduate_order == "extra") %>% 
        arrange(desc(graduate)) %>% 
        select(graduate, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>


### *R* Flipped Class

This course includes the `learnSTATS` package, which can be found at: https://github.com/doomlab/learnSTATS

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(graduate_order != "extra") %>% 
        filter(page == "gradflip") %>% 
        arrange(-desc(as.numeric(graduate_order))) %>%
        select(graduate, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary>

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(graduate_order == "extra") %>% 
        filter(page == "gradflip") %>% 
        arrange(desc(graduate)) %>% 
        select(graduate, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>

### *R* 

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(graduate_order != "extra") %>% 
        filter(page != "gradflip" | is.na(page)) %>% 
        arrange(-desc(as.numeric(graduate_order))) %>%
        select(graduate, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

#### Extra Videos

<details>

  <summary>
  Click to see video list.
  </summary> 

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
        filter(program == "R" | program == "na") %>% 
        filter(graduate_order == "extra") %>% 
        filter(page != "gradflip" | is.na(page)) %>% 
        arrange(desc(graduate)) %>% 
        select(graduate, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```

</details>