---
comments: false
pagetitle: 'Natural Language Modeling'
---

## Natural Language Processing

**Course description:** Web technologies based on text and Natural Language Processing (NLP) are becoming the backbone of analytic solutions for understanding language as text language processing has come to play a central role in the multilingual information society. This course provides a highly accessible introduction to the field of text analytics focusing on processing text, tokenization, entity recognition, classification, and sentiment analysis. The course is intensely practical, it uses *R* and Python programming languages to perform NLP tasks.

- **Cite**: Buchanan, E. M. (2020, March 15). Natural Language Processing in Python (ANLY 520). https://doi.org/10.17605/OSF.IO/ZYKMB 
- **OSF Page**: https://osf.io/zykmb/
- **GitHub Page**: https://github.com/doomlab/statsofdoom-files/tree/master/nlp

```{r echo = F, message = F}
library(rio)
library(kableExtra)
library(dplyr)
page <- "nlp"

yt_data <- import(paste0(here::here(), "/no_sync/youtube_updated.xlsx"))

yt_data <- subset(yt_data, page == page)
```

```{r echo = F, results = 'asis', warning = F}
kable(yt_data %>% 
       #filter(program == "SPSS" | program == "na") %>% 
        filter(order != "extra") %>% 
        arrange(-desc(as.numeric(order))) %>%
        select(section, title, link, materials, person, year_taught),
      col.names = c("Section", "Title", "Link", "Materials", "Person", "Year Taught")) %>% 
  kable_styling(bootstrap_options = c("hover"), font_size = 13)
```
